Array

### 2013-12-17 PAPERS/Report/AdvancedTypes/AdvancedTypes.tex
Fixing the rules to support Array multidimensional. It is not finished, but it is almost there.

%TODO Review the text before present to David

@@

\subsection{Draft of Rules}

@@

The assignment target may be either local to the operation or a state
variable. In the former case, it can be referenced by the corresponding LLVM
identifier. In the latter case, it is represented as an element of the state
structure $\Sigma$, and its address must be calculated and assigned to a new temporary
variable.
\begin{align*}
\lefteqn{\trad{n}{lvalue} \isdef} \\
& \LET t = \llvm{"\PH{\trad{\B{n.type}}{Type}} *"} \IN \\
& \quad \IF \mbox{\B{n} is a local variable} \THEN \llvm{""} \sep \local(\B{n}) \sep t \\
& \quad \IF \mbox{\B{n} is an array} \THEN \LET v = \variable \IN \\
& \quad \quad \llvm{"\PH{v} = getelementptr \PH{\state(\B{n.root})}* \%self\$,\stateindex(\B{n.index,n.type})  \nl"}\\
& \quad \quad \sep v \sep t \\
& \quad \ELSE \LET v = \variable \IN \\
& \quad \quad \llvm{"\PH{v} = getelementptr \PH{\state(\B{n.root})}* \%self\$,} \\
& \quad \quad \quad \llvm{i32 0, i32 \PH{\idx(\B{n})} \nl"} \sep v \sep t
\end{align*}

@@

\begin{minted}[frame=single,bgcolor=bg,linenos=true]{pascal}
Year : struct(
	Year_number : INT,
	Leap_year : BOOL,
	Number_of_days : (1..12) * (28..31),
	Weather : struct( Average_Temperature : (1..12) *  INT,
		Average_Rain : (1..12) * INT) )
\end{minted}

@@

This code stores a value in the record and get the value of element.
%TODO example getting
\begin{minted}[frame=single,bgcolor=bg,linenos=true]{pascal}

%TODO example setting

@@

\subsection{A very simple and generic example}

\begin{minted}[frame=single,bgcolor=bg,linenos=true]{pascal}
MACHINE
   Array(maxindex, TYPE)
CONSTRAINTS maxindex : NAT
VARIABLES arr
INVARIANT arr : 1..maxindex +-> TYPE
INITIALISATION arr := {}
OPERATIONS

set(ix,tt)=
        PRE ix : 1..maxindex & tt : TYPE
        THEN arr := arr <+ {ix |-> tt}
        END ;

tt <-- read(ix) =
        PRE ix : dom (arr)
        THEN tt := arr(ix)
        END;

swap(ix, jx)=
        PRE ix : dom(arr) & jx : dom(arr)
        THEN arr := arr <+ {ix |-> arr(jx), jx|-> arr(ix)}
        END

END
\end{minted}
%\fi
\subsection{A  simple example and its LLVM-IR}
\footnotesize{
\begin{minted}[frame=single,bgcolor=bg,linenos=true]{pascal}
MACHINE
   Array
VARIABLES arr

>>>>

@@

%TODO update the text showing that to get the address is needed to get a 
%sequence of steps.

\subsection{Rules}

@@

TODO: This function updates the Name function ?
TODO: Integrate with EXPArray
% Rule to get a element in array, it can be used in become equal or Expressions
\begin{align*}
\lefteqn{\trad{n}{lvalue} \isdef} \\
& \LET t = \llvm{"\PH{\trad{\B{n.type}}{Type}} *"} \IN \\
& \quad \IF \mbox{\B{n} is a local variable} \THEN \llvm{""} \sep \local(\B{n}) \sep t \\
& \quad \IF \mbox{\B{n} is an array} \THEN \LET v = \variable \IN \trad{n}{AccessArray}  \sep v \sep t \\
& \quad \ELSE \LET v = \variable \IN \\
& \quad \quad \llvm{"\PH{v} = getelementptr \PH{\state(\B{n.root})}* \%self\$,} \\
& \quad \quad \quad \llvm{i32 0, i32 \PH{\idx(\B{n})} \nl"} \sep v \sep t
\end{align*}

%The new rule created 
%It can appear in LHS or RHS in become equal 
% We cannot use the tal function, because it is not able to solve any 
% expressions.
 - Não poderemos usar a função Tal, pois ela não resolverá expressões quaisquer!
\begin{align*}
\lefteqn{\trad{n}{AccessArray} \isdef} \\
&  \LET p_1 \sep v_1 \sep t_1  = \trad{base}{Exp}  \IN \\
&  \LET p_2 \sep v_2 \sep t_2  = \trad{indices}{Exp}  \IN \\
&  \LET v =  \variable  \IN \\
&  \llvm{"\PH{p_1} \PH{p_2} \PH{v} =  getelementptr \PH{t_1}, \PH{v_1}, i32 0, 
i32  \PH{v_2}\nl"} \sep v\\
&  \llvm{"\PH{v} = getelementptr \PH{\state(\B{n.root})}* \%self\$,\stateindex(\B{n.index,n.type})  \nl"}\\
\end{align*}

The assignment target may be either local to the operation or a state
variable. In the former case, it can be referenced by the corresponding LLVM
identifier. In the latter case, it is represented as an element of the state
structure $\Sigma$, and its address must be calculated and assigned to a new temporary
variable.

@@

%TODO update this example
\begin{minted}[frame=single,bgcolor=bg,linenos=true]{pascal}
Year : struct(
	Year_number : INT,
	Leap_year : BOOL,
	Number_of_days : (1..12) * (28..31),
	Weather : struct( Average_Temperature : (1..12) *  INT,
		Average_Rain : (1..12) * INT) )
\end{minted}

@@

This code stores a value in the record and get the value of element.

@@

\subsection{A  simple example and its LLVM-IR}
\footnotesize{
\begin{minted}[frame=single,bgcolor=bg,linenos=true]{pascal}
MACHINE
   Array
VARIABLES arr
